---
title: "Pizzia Analytics"
author: "David Jackson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(scales)
library(DBI)
library(odbc)
library(janitor)
library(lubridate)
library(explore)

```

## Import and Clean Data

```{r}
rm(list=ls())
# Order Types
details <- read_csv("./Data/order_details.csv") %>% clean_names() 
```
```{r}
# Orders
orders <- read_csv("./Data/orders.csv") %>% clean_names()
orders$WDay <- wday(orders$date,label = TRUE)
orders$Hour <- hour(orders$time)
orders$Month <- month(orders$date,label = TRUE)
```
```{r}
# Pizzia Types
ptypes <- read_csv("./Data/pizza_types.csv") %>% clean_names()
```
```{r}
# Pizzas
pizzas <- read_csv("./Data/pizzas.csv") %>% clean_names()
```

### Upload Data to SQL Server 2019

```{r}
## https://db.rstudio.com/databases/microsoft-sql-server/
con <- DBI::dbConnect(odbc::odbc(), 
                      Driver = "SQL Server", 
                      Server = "localhost\\SQLEXPRESS", 
                      Database = "mavenanalytics", 
                      Trusted_Connection = "True")
```

```{r}
# Write Tables
dbWriteTable(con, "details",details ,overwrite=TRUE)
dbListFields(con,"details")
```
```{r}
# Write Tables
dbWriteTable(con, "orders",orders ,overwrite=TRUE)
dbListFields(con,"orders")
```
```{r}
# Write Tables
dbWriteTable(con, "pizzas",pizzas ,overwrite=TRUE)
dbListFields(con,"pizzas")
```
```{r}
# Write Tables
dbWriteTable(con, "ptypes",ptypes ,overwrite=TRUE)
dbListFields(con,"ptypes")
```

## Requirements

Here are some questions that we'd like to be able to answer:

* What days and times do we tend to be busiest?
* How many pizzas are we making during peak periods?
* What are our best and worst selling pizzas?
* What's our average order value?
* How well are we utilizing our seating capacity? (we have 15 tables and 60 seats)
* That's all I can think of for now, but if you have any other ideas I'd love to hear them – you're the expert!

### Quick EDA
```{r}
orders %>% count(date) %>% ggplot() + geom_line(aes(x=date, y=n)) + geom_smooth(aes(x=date, y=n))
```
```{r}
orders %>% count(WDay) %>% ggplot() + geom_col(aes(x=WDay,y=n))
```
```{r}
orders %>% count(Hour) %>% ggplot() + geom_col(aes(x=Month,y=n))
```
```{r}
orders %>% count(Month) %>% ggplot() + geom_col(aes(x=Month,y=n))
```

## Join on pizzia type between details and ptypes

```{r}
ptypes %>% left_join(details,by = c("pizza_type_id" = "pizza_id"))
```

```{r}
details %>% count(pizza_id)
```

